---
title: "Getting Started Doc"
author: "Michael Sieler"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document: 
    toc: yes
    toc_depth: 3
    number_sections: yes
    theme: united
    highlight: tango
  pdf_document: 
    toc: yes
    toc_depth: '3'
    
---

This is a template document to get you started. 

## Troubleshooting:
* Make sure you have all libraries installed, otherwise the loading functions will fail
* Path names will fail if your `.Rproj` file is not located in the top level of you project repository
  * For example, it should be located here: `/Path_to_Project/ProjectName/<name_of_project>.Rproj`


## Setup environment

This is an example chunk of code for setting up your environment prior to running your analysis scripts. You'll want to run this at the top of your analysis scripts.

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, comment = NA, 
                      fig.width = 6.25, fig.height = 5)

# Check project file location is in correct directory
proj.path <- getwd()

# SourceFolder function
source(paste0(proj.path,"/Code/Functions/StartFunctions/sourceFolder.R"))

# Import all helper functions found in `/Functions`
sourceFolder(paste0(proj.path,"/Code/Functions"), T)


# Load Starting Scripts/Functions
start.files <- paste0(file.path(proj.path, list.files(paste0(proj.path,"/Code/Functions/StartFunctions"))))

# Important Paths
path.code <- paste0(proj.path,"/Code")
path.data <- paste0(proj.path,"/Data")
path.rObjects <- paste0(path.data, "/R_objects")
path.input <- paste0(proj.path,"/Data/Input") 
path.results <- paste0(proj.path,"/Results") 
path.figures <- paste0(proj.path, "/Manuscript/Figures")

# Save Environment
# save_env(objects.path, ID = analysis.ID, extra_info = "_pipeline_output")

gg_record(dir = file.path(path.figures, "gg_Record"),
            device = "png")

```

## Post-Dada2 Processing

This script cleans up the Phyloseq object for downstream analysis
 - Loads Phyloseq with cleaned metadata
 - Rarefies, CLR transforms Phyloseq object
 - Outputs a rarefied and CLR-transformed Phyloseq object in the `/Input` directory


```{r}

source(paste0(path.code,"/Functions/AnalysisFunctions/postDada2Functions.R"))

```

