---
title: "Diet_4mo_Physiology"
author: "Michael Sieler"
date: "2022-12-09"
output: html_document
---

This document contains analyses related to the 7 month sampling timepoint comparing control fish fed the three diets. 


```{r}

knitr::opts_chunk$set(
  echo = FALSE,
  cache = FALSE,
  warning = FALSE,
  message = FALSE, 
  # fig.width = 5, fig.height = 5,
  dpi = 300
)



```


## Global Variables

This chunk of code grabs the relevant data frames/tables generated from the `microbiomeProcessing.R` script for analysis.

```{r}

data <- df.conT1
data.alpha <- dt.alphaPlus.conT1.melt
ps.obj <- ps.conT1
dist <- distList.conT1
data.diffAb <- diffAb.conT1

levels(data.alpha$Diet) <- factor(levels(data.alpha$Diet), levels = c("Gemma", "Watts", "ZIRC"))
data.alpha$Diet <- relevel(factor(data.alpha$Diet), ref = "Gemma")

```


### Physiology

This chunk of code outputs figures generated in subsequent chunks into relavent figure folder.

```{r}
# Plot output settings
tmp.path <- "gg_Record/Diet_7moCtrl/Physiology"
gg_record(dir = file.path(path.figures, tmp.path),
          device = "png",
          width = 5,
          height = 5,
          units = "in"
          )

```


#### Weight

##### Diet


```{r Diet-Physio-Weight}

test <- data %>%
  # group_by(Diet) %>%
  rstatix::wilcox_test(data =., Weight ~ Diet) %>%
  rstatix::adjust_pvalue(method = "BH") %>%
  rstatix::add_significance("p.adj")

Fig.1.a <- 
  data %>%
    ggplot(aes(x = Diet, 
               y = Weight
               )) +
    geom_boxplot(aes(fill = Diet)) +
    geom_quasirandom(size = 1) +
    # facet_grid(as.formula(paste0(facet.var.y, " ~ ", facet.var.x)), scales = "free_y") + 
    scale_fill_manual(values = pal.Dark2) +
    scale_color_manual(values = pal.Dark2) + 
    labs(
      # title = "",
      caption = "7mo, control",
      x = "Diet",
      y = "Weight (mg)"
    ) +
    ggpubr::stat_pvalue_manual(test, 
                               label = "p.adj.signif", 
                               size = 6,
                               bracket.size = 1,
                               y.position = c(400, 600, 525)) +
    scale_y_continuous(breaks = scales::breaks_pretty(n = 5), 
                       limits = c(0, 625)) + 
  theme(legend.position = "none")


Fig.1.a

test %>% 
  flextable() %>%
  align(j = 3:6, align = "right") %>%
  colformat_double(j = 6:7, digits = 3) %>%
  merge_v(j = 1) %>%
  set_formatter(values = list("p" = p_val_format,
                              "p.adj" = p_val_format) ) %>%
  set_caption(paste0("Wilcoxon Test. p. adj: BH. Weight ~ Diet")) %>%
  autofit() %>%
  save_as_image(path = file.path(path.figures, tmp.path, "Wilcox_Weight-Diet_7moCtrl.png"))


```

##### (SM) Sex

```{r Sex-Physio-Weight}

test <- data %>%
  # group_by(Diet) %>%
  rstatix::wilcox_test(data =., Weight ~ Sex) %>%
  rstatix::adjust_pvalue(method = "BH") %>%
  rstatix::add_significance("p.adj")

Supp.Fig.1.a <- 
  data %>%
    ggplot(aes(x = Sex, 
               y = Weight
               )) +
    geom_boxplot(aes(fill = Sex)) +
    geom_quasirandom(size = 1) +
    # facet_grid(as.formula(paste0(facet.var.y, " ~ ", facet.var.x)), scales = "free_y") + 
    scale_fill_manual(values = pal.Dark2) +
    scale_color_manual(values = pal.Dark2) + 
    labs(
      # title = "",
      caption = "7mo, control",
      x = "Diet",
      y = "Weight (mg)"
    ) +
    ggpubr::stat_pvalue_manual(test, 
                               label = "p.adj.signif", 
                               size = 6,
                               bracket.size = 1,
                               y.position = c(500)) +
    scale_y_continuous(breaks = scales::breaks_pretty(n = 5), 
                       limits = c(0, 525)) + 
  theme(legend.position = "none")


Supp.Fig.1.a

test %>% 
  flextable() %>%
  align(j = 3:6, align = "right") %>%
  colformat_double(j = 6:7, digits = 3) %>%
  merge_v(j = 1) %>%
  set_formatter(values = list("p" = p_val_format,
                              "p.adj" = p_val_format) ) %>%
  set_caption(paste0("Wilcoxon Test. p. adj: BH. Weight ~ Sex")) %>%
  autofit() %>%
  save_as_image(path = file.path(path.figures, tmp.path, "Wilcox_Weight-Sex_7moCtrl.png"))


```

#### Weight ~ Diet:Sex


```{r Diet-Physio-Weight}

test <- data %>%
  group_by(Sex) %>%
  rstatix::wilcox_test(data =., Weight ~ Diet) %>%
  rstatix::adjust_pvalue(method = "BH") %>%
  rstatix::add_significance("p.adj")

# Fig.1.a <- 
  data %>%
    ggplot(aes(x = Diet, 
               y = Weight,
               # fill = Sex
               )) +
    geom_boxplot(aes(fill=Sex)) +
    geom_quasirandom(aes(fill=Sex), shape = 21, dodge.width=.75) +
    # facet_grid(as.formula(paste0(facet.var.y, " ~ ", facet.var.x)), scales = "free_y") + 
    scale_fill_manual(values = pal.Dark2) +
    scale_color_manual(values = pal.Dark2) + 
    labs(
      # title = "",
      caption = "7mo, control",
      x = "Diet",
      y = "Weight (mg)"
    ) +
    ggpubr::stat_pvalue_manual(test,
                               label = "p.adj.signif",
                               size = 6,
                               bracket.size = 1,
                               y.position = c(375, 550, 450)
                               ) +
    scale_y_continuous(breaks = scales::breaks_pretty(n = 5),
                       limits = c(0, 575)) +
  theme(legend.position = "bottom")


# Fig.1.a

test %>% 
  flextable() %>%
  align(j = 3:6, align = "right") %>%
  colformat_double(j = 6:7, digits = 3) %>%
  merge_v(j = 1) %>%
  set_formatter(values = list("p" = p_val_format,
                              "p.adj" = p_val_format) ) %>%
  set_caption(paste0("Wilcoxon Test. p. adj: BH. Weight ~ Diet*Sex")) %>%
  autofit() %>%
  save_as_image(path = file.path(path.figures, tmp.path, "Wilcox_Weight-DietSex_7moCtrl.png"))


```



#### Body Condition Score

##### Diet

```{r Diet-Physio-BCS}
test <- data %>%
  # group_by(Diet) %>%
  rstatix::wilcox_test(data =., Body.Condition.Score ~ Diet) %>%
  rstatix::adjust_pvalue(method = "BH") %>%
  rstatix::add_significance("p.adj")


Fig.1.b <- 
  data %>%
    ggplot(aes(x = Diet, 
               y = Body.Condition.Score
               )) +
    geom_boxplot(aes(fill = Diet)) +
    geom_quasirandom(size = 1) +
    # facet_grid(as.formula(paste0(facet.var.y, " ~ ", facet.var.x)), scales = "free_y") + 
    scale_fill_manual(values = pal.Dark2) +
    scale_color_manual(values = pal.Dark2) + 
    labs(
      # title = "",
      caption = "7mo, control",
      x = "Diet",
      y = "Body Condition Score"
    ) +
    ggpubr::stat_pvalue_manual(test, 
                               label = "p.adj.signif", 
                               size = 6,
                               bracket.size = 1,
                               y.position = c(2.75, 3, 3.25)) +
    scale_y_continuous(breaks = scales::breaks_pretty(n = 5), 
                       limits = c(1, 3.5)) + 
  theme(legend.position = "none")

Fig.1.b

test %>% 
  flextable() %>%
  align(j = 3:6, align = "right") %>%
  colformat_double(j = 6:7, digits = 3) %>%
  merge_v(j = 1) %>%
  set_formatter(values = list("p" = p_val_format,
                              "p.adj" = p_val_format) ) %>%
  set_caption(paste0("Wilcoxon Test. p. adj: BH. Body.Condition.Score ~ Diet")) %>%
  autofit() %>%
  save_as_image(path = file.path(path.figures, tmp.path, "Wilcox_BCS-Diet_7moCtrl.png"))

```

##### (SM) Sex

```{r Sex-Physio-Weight}

test <- data %>%
  # group_by(Diet) %>%
  rstatix::wilcox_test(data =., Body.Condition.Score ~ Sex) %>%
  rstatix::adjust_pvalue(method = "BH") %>%
  rstatix::add_significance("p.adj")

Supp.Fig.1.b <- 
  data %>%
    ggplot(aes(x = Sex, 
               y = Body.Condition.Score
               )) +
    geom_boxplot(aes(fill = Sex)) +
    geom_quasirandom(size = 1) +
    # facet_grid(as.formula(paste0(facet.var.y, " ~ ", facet.var.x)), scales = "free_y") + 
    scale_fill_manual(values = pal.Dark2) +
    scale_color_manual(values = pal.Dark2) + 
    labs(
      # title = "",
      caption = "7mo, control",
      x = "Diet",
      y = "Body Condition Score"
    ) +
    ggpubr::stat_pvalue_manual(test, 
                               label = "p.adj.signif", 
                               size = 6,
                               bracket.size = 1,
                               y.position = c(4)) +
    scale_y_continuous(breaks = scales::breaks_pretty(n = 5), 
                       limits = c(0, 4)) + 
  theme(legend.position = "none")


Supp.Fig.1.b

test %>% 
  flextable() %>%
  align(j = 3:6, align = "right") %>%
  colformat_double(j = 6:7, digits = 3) %>%
  merge_v(j = 1) %>%
  set_formatter(values = list("p" = p_val_format,
                              "p.adj" = p_val_format) ) %>%
  set_caption(paste0("Wilcoxon Test. p. adj: BH. Body.Condition.Score ~ Sex")) %>%
  autofit() %>%
  save_as_image(path = file.path(path.figures, tmp.path, "Wilcox_BCS-Sex_7moCtrl.png"))


```
