---
title: "Diet_4mo_Physiology"
author: "Michael Sieler"
date: "2022-12-09"
output: html_document
---

This document contains analyses related to the 4 and 7 month sampling timepoints comparing control fish fed the three diets. 


```{r}

knitr::opts_chunk$set(
  echo = FALSE,
  cache = FALSE,
  warning = FALSE,
  message = FALSE, 
  # fig.width = 5, fig.height = 5,
  dpi = 300
)



```


## Global Variables

This chunk of code grabs the relevant data frames/tables generated from the `microbiomeProcessing.R` script for analysis.

```{r}

data <- df.conT0T1
data.alpha <- dt.alphaPlus.conT0T1.melt
ps.obj <- ps.conT0T1
dist <- distList.conT0T1
# data.diffAb <- diffAb.conT0T1_DietTime
# data.diffAb <- diffAb.conT0T1_Time

levels(data.alpha$Timepoint) <- factor(levels(data.alpha$Timepoint), levels = c("4mpf", "7mpf"))
data.alpha$Timepoint <- relevel(factor(data.alpha$Timepoint), ref = "4mpf")

levels(data$Timepoint) <- factor(levels(data$Timepoint), levels = c("4mpf", "7mpf"))
data$Timepoint <- relevel(factor(data$Timepoint), ref = "4mpf")

```



### Beta Diversity


```{r}
tmp.path <- "gg_Record/Dev_4mo7moCtrl/Beta"
# Plot settings
gg_record(dir = file.path(path.figures, tmp.path),
          device = "png",
          width = 5,
          height = 5,
          units = "in"
          )

```

#### Diet

```{r Dev-Beta-Diets}

# Full dbRDA models
mod <- full_dbrda_model(vars = c("Diet"),  # Enter variables as a list "c(var.A, var.B, var.C)"
                          distance = dist,
                          methods = methods.beta,
                          names = set_names_beta,
                          physeq = ps.obj,
                          data = data,
                          terms = 1,  # if you want interaction terms enter 2, otherwise 1
                          num.cores = num.cores
                        )

anova <- beta_anova(beta.model = mod,
                    methods = methods.beta,
                    names = set_names_beta,
                    num.cores = num.cores)


# Plot prep
dt.ord.full.beta <- ord_dt_list(mod, ps.obj)
beta.dt.full <- samp_coord_dt(dt.ord.full.beta, methods.beta)
beta.axis.full <- axis_labels(dt.ord.full.beta)

# lapply(methods.beta, function(beta){
# 
# p.val <- anova$p.value[anova$metric == beta][1]
# p.val.label <- paste0("p-value", ifelse(p.val == 0.001, " < ", " = " ), p.val)
# cap.min <- min(dt.ord.full.beta[[beta]]$sample.coords[[3]])
# cap.max <- max(dt.ord.full.beta[[beta]]$sample.coords[[2]])
# 
# 
#   dt.ord.full.beta[[beta]]$sample.coords %>%
#     ggplot(aes(x = .[[2]], y = .[[3]])) +
#       stat_ellipse(aes(color = Diet )) +
#       geom_point(aes(color = Diet),
#                  size = 2.5,
#                  alpha = 1) +
#       annotate("text", 
#                label = p.val.label,
#                x = cap.max, y = cap.min, 
#                size = 5, 
#                color = "black",
#                hjust = .95
#       ) +
#       scale_fill_manual(values = col.Diet) +
#       scale_color_manual(values = col.Diet)  + 
#       labs(x = dt.ord.full.beta[[beta]]$axes.labs[1], 
#            y = dt.ord.full.beta[[beta]]$axes.labs[2],
#            caption = beta) + 
#       theme(legend.position = "bottom")
# })



# Fig.2.c <- lapply(methods.beta, function(beta){
# 
# p.val <- anova$p.value[anova$metric == beta][1]
# p.val.label <- paste0("p-value", ifelse(p.val == 0.001, " < ", " = " ), p.val)
# cap.min <- min(dt.ord.full.beta[[beta]]$sample.coords[[3]])
# cap.max <- max(dt.ord.full.beta[[beta]]$sample.coords[[2]])
# 
# 
#   dt.ord.full.beta[[beta]]$sample.coords %>%
#     ggplot(aes(x = .[[2]], y = .[[3]])) +
#       stat_ellipse(aes(color = Timepoint )) +
#       geom_point(aes(color = Timepoint),
#                  size = 2.5,
#                  alpha = 1) +
#       annotate("text", 
#                label = p.val.label,
#                x = cap.max, y = cap.min, 
#                size = 5, 
#                color = "black",
#                hjust = .95
#       ) +
#       scale_fill_manual(values = col.Time) +
#       scale_color_manual(values = col.Time)  + 
#       labs(x = dt.ord.full.beta[[beta]]$axes.labs[1], 
#            y = dt.ord.full.beta[[beta]]$axes.labs[2],
#            caption = beta) + 
#       theme(legend.position = "bottom")
# })

lapply(methods.beta, function(beta){

  p.val <- anova$p.value[anova$metric == beta][1]
  p.val.label <- paste0("p-value", ifelse(p.val == 0.001, " < ", " = " ), p.val)
  cap.min <- min(dt.ord.full.beta[[beta]]$sample.coords[[3]])
  cap.max <- max(dt.ord.full.beta[[beta]]$sample.coords[[2]])

  dt.ord.full.beta[[beta]]$sample.coords %>%
    ggplot(aes(x = .[[2]], y = .[[3]])) +
      stat_ellipse(aes(color = Diet )) +
      geom_point(aes(color = Diet,
                     shape = Timepoint),
                 stroke = 1,
                 size = 2.5,
                 alpha = 1) +
      annotate("text", 
               label = p.val.label,
               x = cap.max, y = cap.min, 
               size = 5, 
               color = "black",
               hjust = .95
      ) +
      scale_fill_manual(name = "Time", values = col.Diet) +
      scale_color_manual(name = "Time", values = col.Diet)  + 
      scale_shape_manual(name = "Time", values = c(19, 1)) +
      labs(x = dt.ord.full.beta[[beta]]$axes.labs[1], 
           y = dt.ord.full.beta[[beta]]$axes.labs[2],
           caption = beta) + 
      theme(legend.position = "bottom")
})

# Fig.2.c.3 <- lapply(methods.beta, function(beta){
# 
# p.val <- anova$p.value[anova$metric == beta][1]
# p.val.label <- paste0("p-value", ifelse(p.val == 0.001, " < ", " = " ), p.val)
# cap.min <- min(dt.ord.full.beta[[beta]]$sample.coords[[3]])
# cap.max <- max(dt.ord.full.beta[[beta]]$sample.coords[[2]])
# 
# 
#   dt.ord.full.beta[[beta]]$sample.coords %>%
#     ggplot(aes(x = .[[2]], y = .[[3]])) +
#       stat_ellipse(aes(color = Diet )) +
#       geom_point(aes(color = Diet, fill = Timepoint),
#                  shape = 21,
#                  size = 2.5,
#                  stroke = 1.25,
#                  alpha = 1) +
#       annotate("text", 
#                label = p.val.label,
#                x = cap.max, y = cap.min, 
#                size = 5, 
#                color = "black",
#                hjust = .95
#       ) +
#       scale_fill_manual(name = "Time", values = col.Time) +
#       scale_color_manual(name = "Diet",values = col.Diet)  + 
#       labs(x = dt.ord.full.beta[[beta]]$axes.labs[1], 
#            y = dt.ord.full.beta[[beta]]$axes.labs[2],
#            caption = beta) + 
#       theme(legend.position = "bottom")
# })



stats_table(anova) %>%
  set_caption(paste0("Distance-based redundancy analysis (dbRDA) ordination. Beta.Score ~ Diet")) %>%
  save_as_image(path = file.path(path.figures, tmp.path, "dbRDA_ANOVA_Beta-Diet_4-7moCtrl.png"))


```



#### Time

```{r Dev-Beta-Time}


# Full dbRDA models
mod <- full_dbrda_model(vars = c("Timepoint"),  # Enter variables as a list "c(var.A, var.B, var.C)"
                          distance = dist,
                          methods = methods.beta,
                          names = set_names_beta,
                          physeq = ps.obj,
                          data = data,
                          terms = 1,  # if you want interaction terms enter 2, otherwise 1
                          num.cores = num.cores
                        )

anova <- beta_anova(beta.model = mod,
                    methods = methods.beta,
                    names = set_names_beta,
                    num.cores = num.cores)


# Plot prep
dt.ord.full.beta <- ord_dt_list(mod, ps.obj)
beta.dt.full <- samp_coord_dt(dt.ord.full.beta, methods.beta)
beta.axis.full <- axis_labels(dt.ord.full.beta)

# lapply(methods.beta, function(beta){
# 
#   p.val <- anova$p.value[anova$metric == beta][1]
#   p.val.label <- paste0("p-value", ifelse(p.val == 0.001, " < ", " = " ), p.val)
#   cap.min <- min(dt.ord.full.beta[[beta]]$sample.coords[[3]])
#   cap.max <- max(dt.ord.full.beta[[beta]]$sample.coords[[2]])
# 
#   dt.ord.full.beta[[beta]]$sample.coords %>%
#     ggplot(aes(x = .[[2]], y = .[[3]])) +
#       stat_ellipse(aes(color = Diet, linetype = Timepoint )) +
#       geom_point(aes(color = Diet,
#                      shape = Timepoint),
#                  size = 2.5,
#                  alpha = 1) +
#       annotate("text", 
#                label = p.val.label,
#                x = cap.max, y = cap.min, 
#                size = 5, 
#                color = "black",
#                hjust = .95
#       ) +
#       scale_fill_manual(name = "Time", values = col.Time) +
#       scale_color_manual(name = "Diet", values = col.Diet)  + 
#       scale_shape_manual(name = "Time", values = c(19, 1)) +
#       scale_linetype_manual(name = "Time", values = c("solid", "dashed")) +
#       labs(x = dt.ord.full.beta[[beta]]$axes.labs[1], 
#            y = dt.ord.full.beta[[beta]]$axes.labs[2],
#            caption = beta) + 
#       theme(legend.position = "bottom")
# })



lapply(methods.beta, function(beta){

  p.val <- anova$p.value[anova$metric == beta][1]
  p.val.label <- paste0("p-value", ifelse(p.val == 0.001, " < ", " = " ), p.val)
  cap.min <- min(dt.ord.full.beta[[beta]]$sample.coords[[3]])
  cap.max <- max(dt.ord.full.beta[[beta]]$sample.coords[[2]])

  dt.ord.full.beta[[beta]]$sample.coords %>%
    ggplot(aes(x = .[[2]], y = .[[3]])) +
      stat_ellipse(aes(color = Diet )) +
      geom_point(aes(color = Diet,
                     shape = Timepoint),
                 stroke = 1,
                 size = 2.5,
                 alpha = 1) +
      annotate("text", 
               label = p.val.label,
               x = cap.max, y = cap.min, 
               size = 5, 
               color = "black",
               hjust = .95
      ) +
      scale_fill_manual(name = "Time", values = col.Diet) +
      scale_color_manual(name = "Time", values = col.Diet)  + 
      scale_shape_manual(name = "Time", values = c(19, 1)) +
      labs(x = dt.ord.full.beta[[beta]]$axes.labs[1], 
           y = dt.ord.full.beta[[beta]]$axes.labs[2],
           caption = beta) + 
      theme(legend.position = "bottom")
})





stats_table(anova) %>%
  set_caption(paste0("Distance-based redundancy analysis (dbRDA) ordination. Beta.Score ~ Time")) %>%
  save_as_image(path = file.path(path.figures, tmp.path, "dbRDA_ANOVA_Beta-Time_4-7moCtrl.png"))

```


#### Diets:Time


```{r}

# Full dbRDA models
mod <- full_dbrda_model(vars = c("Diet", "Timepoint"),  # Enter variables as a list "c(var.A, var.B, var.C)"
                          distance = dist,
                          methods = methods.beta,
                          names = set_names_beta,
                          physeq = ps.obj,
                          data = data,
                          terms = 2,  # if you want interaction terms enter 2, otherwise 1
                          num.cores = num.cores
                        )

anova <- beta_anova(beta.model = mod,
                    methods = methods.beta,
                    names = set_names_beta,
                    num.cores = num.cores)


# Plot prep
beta.metric <- 'Bray-Curtis'
dt.ord.full.beta <- ord_dt_list(mod, ps.obj)
beta.dt.full <- samp_coord_dt(dt.ord.full.beta, methods.beta)
beta.axis.full <- axis_labels(dt.ord.full.beta)



lapply(methods.beta, function(beta){

  p.val <- anova$p.value[anova$metric == beta][1]
  p.val.label <- paste0("p-value", ifelse(p.val == 0.001, " < ", " = " ), p.val)
  cap.min <- min(dt.ord.full.beta[[beta]]$sample.coords[[3]])
  cap.max <- max(dt.ord.full.beta[[beta]]$sample.coords[[2]])

  dt.ord.full.beta[[beta]]$sample.coords %>%
    ggplot(aes(x = .[[2]], y = .[[3]])) +
      stat_ellipse(aes(color = Diet )) +
      geom_point(aes(color = Diet,
                     shape = Timepoint),
                 stroke = 1,
                 size = 2.5,
                 alpha = 1) +
      annotate("text", 
               label = p.val.label,
               x = cap.max, y = cap.min, 
               size = 5, 
               color = "black",
               hjust = .95
      ) +
      scale_fill_manual(name = "Time", values = col.Diet) +
      scale_color_manual(name = "Time", values = col.Diet)  + 
      scale_shape_manual(name = "Time", values = c(19, 1)) +
      labs(x = dt.ord.full.beta[[beta]]$axes.labs[1], 
           y = dt.ord.full.beta[[beta]]$axes.labs[2],
           caption = beta) + 
      theme(legend.position = "bottom")
})



# 
# Fig.2.x.1 <- lapply(methods.beta, function(beta){
#   
#   p.val <- anova$p.value[anova$metric == beta][1]
#   p.val.label <- paste0("p-value", ifelse(p.val == 0.001, " < ", " = " ), p.val)
#   cap.min <- min(dt.ord.full.beta[[beta.metric]]$sample.coords[[3]])
#   cap.max <- max(dt.ord.full.beta[[beta.metric]]$sample.coords[[2]])
# 
# 
#   dt.ord.full.beta[[beta.metric]]$sample.coords %>%
#     ggplot(aes(x = CAP1, y = CAP2)) +
#       stat_ellipse(aes(color = Diet, linetype = Timepoint )) +
#       geom_point(aes(color = Diet,
#                      shape = Timepoint),
#                  # shape = 21,
#                  size = 2.5,
#                  alpha = 1) +
#       annotate("text", 
#                # label = paste0(beta.metric, "; ", p.val.label),
#                label = p.val.label,
#                x = cap.max, y = cap.min, 
#                size = 5, 
#                color = "black",
#                hjust = .95
#       ) +
#       scale_fill_manual(name = "Diet", values = pal.Dark2) +
#       scale_color_manual(name = "Diet", values = pal.Dark2)  + 
#       scale_shape_manual(name = "Time", values = c(19, 1)) +
#       labs(x = dt.ord.full.beta[[beta.metric]]$axes.labs[1], 
#            y = dt.ord.full.beta[[beta.metric]]$axes.labs[2],
#            caption = beta) + 
#       theme(legend.position = "bottom")
# 
# })
#   
# Fig.2.x.1
# 
# Fig.2.x.2 <- lapply(methods.beta, function(beta){
#   
#   p.val <- anova$p.value[anova$metric == beta.metric][1]
#   p.val.label <- paste0("p-value", ifelse(p.val == 0.001, " < ", " = " ), p.val)
#   cap.min <- min(dt.ord.full.beta[[beta.metric]]$sample.coords[[3]])
#   cap.max <- max(dt.ord.full.beta[[beta.metric]]$sample.coords[[2]])
# 
# 
#   dt.ord.full.beta[[beta.metric]]$sample.coords %>%
#     ggplot(aes(x = .[[2]], y = .[[3]])) +
#       stat_ellipse(aes(color = Timepoint, linetype = Diet )) +
#       geom_point(aes(color = Timepoint,
#                      fill = Timepoint,
#                      shape = Diet
#                      ),
#                  # shape = 21,
#                  size = 2.5,
#                  alpha = 1) +
#       annotate("text", 
#                # label = paste0(beta.metric, "; ", p.val.label),
#                label = p.val.label,
#                x = cap.max, y = cap.min, 
#                size = 5, 
#                color = "black",
#                hjust = .95
#       ) +
#       scale_fill_manual(name = "Diet", values = col.Time) +
#       scale_color_manual(name = "Diet", values = col.Time)  + 
#       # scale_shape_manual(name = "Time", values = c(19, 1)) +
#       labs(x = dt.ord.full.beta[[beta.metric]]$axes.labs[1], 
#            y = dt.ord.full.beta[[beta.metric]]$axes.labs[2],
#            caption = beta) + 
#       theme(legend.position = "bottom")
# 
# })
#   
# Fig.2.x.2


stats_table(anova) %>%
  set_caption(paste0("Distance-based redundancy analysis (dbRDA) ordination. Beta.Score ~ Diet*Time")) %>%
  save_as_image(path = file.path(path.figures, tmp.path, "dbRDA_ANOVA_Beta-DietTime_4-7moCtrl.png"))

```





#### (SM) Beta-Dispersion

```{r}
ord.beta <- c("bray", "canberra", "sor")

data.beta <- lapply(ord.beta, function(beta){
  
  tmp.ord <- phyloseq::ordinate(
      physeq = ps.obj, 
      method = "PCoA",  # c("DCA", "CCA", "RDA", "CAP", "DPCoA", "NMDS", "MDS", "PCoA")
      distance = beta  # c("bray", "canberra", "sor")
    )
  
  tmp.ord.data <- list()
  tmp.ord.data[[beta]] <- phyloseq::plot_ordination(
      physeq = ps.obj,
      ordination = tmp.ord,
      justDF = T
    )
  
}) %>% set_names(ord.beta)

```


##### Diet

```{r, fig.width=5, fig.height=5}

# Beta-dispersion Table
ord.beta <- c("bray", "canberra", "sor")
beta.disp <- list()
beta.disp.stats <- list()
beta.disp <- lapply(dist, function(beta) {
  set.seed(42)
  betadisper(beta, group = data$Diet)  %>% permutest(pairwise = T, permutations = 999)
  
}) %>% setNames(ord.beta)

lapply(dist, function(beta) {
  set.seed(42)
  betadisper(beta, group = data$Diet)  %>% boxplot(xlab = "Diet")
  
}) 

# Anova
beta.disp.stats[["anova"]] <- lapply(beta.disp, function(beta) {
  beta$tab %>% 
    flextable()
}) %>% setNames(methods.beta)

# Permutation table
beta.disp.stats[["pairwise"]] <-lapply(beta.disp, function(beta) {
  # print(beta)
  beta$pairwise$permuted %>%
    tidy() %>%
    rename(Names = names,
           `p-value` = x) %>%
    flextable()
}) %>% setNames(methods.beta)

lapply(c("anova", "pairwise"), function(x){
  lapply(beta.disp.stats[x], function(test){
    lapply(methods.beta, function(beta){
  beta.disp.stats[[x]][[beta]] %>%
  save_as_image(path = file.path(path.figures, tmp.path, paste0("Disp_Beta-", x, "-",beta, "-Diet_4-7moCtrl.png"))
                )
   })
  })
})
```


##### Time

```{r, fig.width=5, fig.height=5}

# Beta-dispersion Table
ord.beta <- c("bray", "canberra", "sor")
beta.disp <- list()
beta.disp.stats <- list()
beta.disp <- lapply(dist, function(beta) {
  set.seed(42)
  betadisper(beta, group = data$Timepoint)  %>% permutest(pairwise = T, permutations = 999)
  
}) %>% setNames(ord.beta)

lapply(dist, function(beta) {
  set.seed(42)
  betadisper(beta, group = data$Timepoint)  %>% boxplot(xlab = "Time")
  
}) 

# Anova
beta.disp.stats[["anova"]] <- lapply(beta.disp, function(beta) {
  beta$tab %>% 
    flextable()
}) %>% setNames(methods.beta)

# Permutation table
beta.disp.stats[["pairwise"]] <-lapply(beta.disp, function(beta) {
  # print(beta)
  beta$pairwise$permuted %>%
    tidy() %>%
    rename(Names = names,
           `p-value` = x) %>%
    flextable()
}) %>% setNames(methods.beta)

lapply(c("anova", "pairwise"), function(x){
  lapply(beta.disp.stats[x], function(test){
    lapply(methods.beta, function(beta){
  beta.disp.stats[[x]][[beta]] %>%
  save_as_image(path = file.path(path.figures, tmp.path, paste0("Disp_Beta-", x, "-",beta, "-Time_4-7moCtrl.png"))
                )
   })
  })
})
```

##### Diet:Time (all)

```{r}

# Add interaction
tmp.data <- data %>%
  mutate(Diet.Time = paste0(Diet,".", Timepoint), .after = Age)

# Beta-dispersion Table
ord.beta <- c("bray", "canberra", "sor")
beta.disp <- list()
beta.disp.stats <- list()
beta.disp <- lapply(dist, function(beta) {
  set.seed(42)
  betadisper(beta, group = tmp.data$Diet.Time)  %>% permutest(pairwise = T, permutations = 999)
  
}) %>% setNames(ord.beta)

lapply(dist, function(beta) {
  set.seed(42)
  betadisper(beta, group = tmp.data$Diet.Time)  %>% boxplot(col = col.Diet[c(1,1,2,2,3,3)],
                                                        xlab = "Time")
  
}) 



# Anova
beta.disp.stats[["anova"]] <- lapply(beta.disp, function(beta) {
  beta$tab %>% 
    flextable()
}) %>% setNames(methods.beta)

# Permutation table
beta.disp.stats[["pairwise"]] <- lapply(beta.disp, function(beta) {
  # print(beta)
  beta$pairwise$permuted %>%
    tidy() %>%
    rename(Names = names,
           `p-value` = x) %>%
    filter(`p-value` < .1) %>%
    arrange(`p-value`) %>%
    flextable() %>%
  set_caption(paste0("filtered p-value < 0.1"))
}) %>% setNames(methods.beta)

lapply(c("anova", "pairwise"), function(x){
  lapply(beta.disp.stats[x], function(test){
    lapply(methods.beta, function(beta){
  beta.disp.stats[[x]][[beta]] %>%
  save_as_image(path = file.path(path.figures, tmp.path, paste0("Disp_Beta-", x, "-",beta, "-DietTime_4-7moCtrl.png"))
                )
   })
  })
})

```


##### Diet:Time (per diet)

###### Gemma

```{r}

# Filter for diet
tmp.data <- data %>%
  filter(Diet == "Gemma")

dist <- distList.conT0T1.Gemma

# Beta-dispersion Table
ord.beta <- c("bray", "canberra", "sor")
beta.disp <- list()
beta.disp.stats <- list()
beta.disp <- lapply(dist, function(beta) {
  set.seed(42)
  betadisper(beta, group = tmp.data$Timepoint)  %>% permutest(pairwise = T, permutations = 999)
  
}) %>% setNames(ord.beta)

lapply(dist, function(beta) {
  set.seed(42)
  betadisper(beta, group = tmp.data$Time)  %>% boxplot(col = col.Diet[1],
                                                        xlab = "Time (Gemma)")
}) 



# Anova
beta.disp.stats[["anova"]] <- lapply(beta.disp, function(beta) {
  beta$tab %>% 
    flextable()
}) %>% setNames(methods.beta)

# Permutation table
beta.disp.stats[["pairwise"]] <-lapply(beta.disp, function(beta) {
  # print(beta)
  beta$pairwise$permuted %>%
    tidy() %>%
    rename(Names = names,
           `p-value` = x) %>%
    flextable()
}) %>% setNames(methods.beta)

lapply(c("anova", "pairwise"), function(x){
  lapply(beta.disp.stats[x], function(test){
    lapply(methods.beta, function(beta){
  beta.disp.stats[[x]][[beta]] %>%
  save_as_image(path = file.path(path.figures, tmp.path, paste0("Disp_Beta-", x, "-",beta, "-DietTime_4-7moCtrl_Gemma.png"))
                )
   })
  })
})


```


###### Watts

```{r}

# Filter for diet
tmp.data <- data %>%
  filter(Diet == "Watts")

dist <- distList.conT0T1.Watts

# Beta-dispersion Table
ord.beta <- c("bray", "canberra", "sor")
beta.disp <- list()
beta.disp.stats <- list()
beta.disp <- lapply(dist, function(beta) {
  set.seed(42)
  betadisper(beta, group = tmp.data$Timepoint)  %>% permutest(pairwise = T, permutations = 999)
  
}) %>% setNames(ord.beta)

lapply(dist, function(beta) {
  set.seed(42)
  betadisper(beta, group = tmp.data$Time)  %>% boxplot(col = col.Diet[2],
                                                        xlab = "Time (Watts)")
}) 



# Anova
beta.disp.stats[["anova"]] <- lapply(beta.disp, function(beta) {
  beta$tab %>% 
    flextable()
}) %>% setNames(methods.beta)

# Permutation table
beta.disp.stats[["pairwise"]] <-lapply(beta.disp, function(beta) {
  # print(beta)
  beta$pairwise$permuted %>%
    tidy() %>%
    rename(Names = names,
           `p-value` = x) %>%
    flextable()
}) %>% setNames(methods.beta)

lapply(c("anova", "pairwise"), function(x){
  lapply(beta.disp.stats[x], function(test){
    lapply(methods.beta, function(beta){
  beta.disp.stats[[x]][[beta]] %>%
  save_as_image(path = file.path(path.figures, tmp.path, paste0("Disp_Beta-", x, "-",beta, "-DietTime_4-7moCtrl_Watts.png"))
                )
   })
  })
})


```



###### ZIRC

```{r}

# Filter for diet
tmp.data <- data %>%
  filter(Diet == "ZIRC")

dist <- distList.conT0T1.ZIRC

# Beta-dispersion Table
ord.beta <- c("bray", "canberra", "sor")
beta.disp <- list()
beta.disp.stats <- list()
beta.disp <- lapply(dist, function(beta) {
  set.seed(42)
  betadisper(beta, group = tmp.data$Timepoint)  %>% permutest(pairwise = T, permutations = 999)
  
}) %>% setNames(ord.beta)

lapply(dist, function(beta) {
  set.seed(42)
  betadisper(beta, group = tmp.data$Time)  %>% boxplot(col = col.Diet[3],
                                                        xlab = "Time (ZIRC)")
}) 



# Anova
beta.disp.stats[["anova"]] <- lapply(beta.disp, function(beta) {
  beta$tab %>% 
    flextable()
}) %>% setNames(methods.beta)

# Permutation table
beta.disp.stats[["pairwise"]] <-lapply(beta.disp, function(beta) {
  # print(beta)
  beta$pairwise$permuted %>%
    tidy() %>%
    rename(Names = names,
           `p-value` = x) %>%
    flextable()
}) %>% setNames(methods.beta)

lapply(c("anova", "pairwise"), function(x){
  lapply(beta.disp.stats[x], function(test){
    lapply(methods.beta, function(beta){
  beta.disp.stats[[x]][[beta]] %>%
  save_as_image(path = file.path(path.figures, tmp.path, paste0("Disp_Beta-", x, "-",beta, "-DietTime_4-7moCtrl_ZIRC.png"))
                )
   })
  })
})


```

